---
title: "STAT40830 - Adv Data Prog With R (online)"
subtitle: "HW Assignment 1"
author: "Deepankar Vyas , 23200527"
date: today
date-format: long
format:
  revealjs: 
    toc: true 
    slide-number: true
    footer: ""
    incremental: false
    fragments: true
    chalkboard: false
    menu: true
    scrollable: true
    preview-links: false
    embed-resources: true
    fontsize: 28pt
    theme: "moon" 
---

## Question Statement

\center 

***Create a neat Quarto document or presentation. In the document/presentation, you must do a plot on a dataset that can be found on any R package and include some text explaining what you plotted. The file does not need to be extensive. If you wish to add some extra text, consider adding an explanation of your approach, some descriptive statistics of the variables used in the graph and a line or two introducing the dataset as part of an introduction.***

## IRIS Dataset

```{r}
#| label: Importing dataset
#| eval: true
#| echo: false

data(iris)

```

- The famous (Fisher's or Anderson's) iris data set gives the measurements in centimeters of different variables. \vspace{2 mm}
- The variables are - sepal length and width and petal length and width, respectively, for `r nrow(iris)` flowers from each of `r length(table(iris$Species))` species of iris. \vspace{2 mm}
- The species are Iris [setosa]{style="color: blue;"}, [versicolor]{style="color: red;"}, and [virginica]{style="color: green;"}.

## Petal Length Vs Petal Width 

```{r}
#| label: Plotting
#| echo: false
#| eval: true

# Define the colors for each species
cols <- c("blue", "red", "green")

# Create a color vector based on species
species_colors <- cols[as.numeric(iris$Species)]

# Create the plot
plot(iris$Petal.Length, iris$Petal.Width, 
     xlab = "Petal Length", 
     ylab = "Petal Width", 
     main = "Petal length vs width", 
     col = species_colors, 
     pch = 19)

# Add legend
legend("topright", 
       legend = levels(iris$Species), 
       col = cols, 
       pch = 19, 
       title = "Species")


```

## Variables' Overview

Here, we have plotted a scatter plot between Petal length and Petal width, coloured by different species, trying to find some patterns. A quick rundown of the 2 variables in question:-

::: columns
::: {.column width="50%"}
Summary of Petal Length:

```{r}
#| label: summary petal length
#| echo: false
as.data.frame(t(summary(iris$Petal.Length)))[,-1]
```
:::

::: {.column width="50%"}
Summary of Petal Width:

```{r}
#| label: summary petal width
#| echo: false
as.data.frame(t(summary(iris$Petal.Width)))[,-1]
```
:::
:::

\vspace{4 mm}

A quick analysis of the graph is as follows:-

## Analysis

1. From the graph, there appears to be a strong positive correlation between petal legth and petal width. \vspace{2 mm}
2. Different species of flowers displays different characterisics.\vspace{2 mm}
3. [Setosa]{style="color: blue;"} generally has lower Petal length and Petal width comparatively. [Versicolor]{style="color: red;"} has higher Petal Length and Petal width compared to [Setosa]{style="color: blue;"} but generally lesser than [Virginica]{style="color: green;"}. [Viriginica]{style="color: green;"} generally tends to have the highest Petal legth and width amongst the `r length(table(iris$Species))` species considered.\vspace{2 mm}
4. More details about the dataset can be found [here](https://en.wikipedia.org/wiki/Iris_flower_data_set)

## Sepal Length vs Sepal Width - plot

```{r}
#| label: Plotting-sepal
#| echo: false
#| eval: true

# Define the colors for each species
cols <- c("blue", "red", "green")

# Create a color vector based on species
species_colors <- cols[as.numeric(iris$Species)]

# Create the plot
plot(iris$Sepal.Length, iris$Sepal.Width, 
     xlab = "Sepal Length", 
     ylab = "Sepal Width", 
     main = "Sepal length vs width", 
     col = species_colors, 
     pch = 19)

# Add legend
legend("topright", 
       legend = levels(iris$Species), 
       col = cols, 
       pch = 19, 
       title = "Species")


```

## Summary statistics of Sepal Length and Sepal Width

::: columns
::: {.column width="50%"}
Summary of Sepal Length:

```{r}
#| label: summary-sepal length
#| echo: false
as.data.frame(t(summary(iris$Sepal.Length)))[,-1]
```
:::

::: {.column width="50%"}
Summary of Sepal Width:

```{r}
#| label: summary sepal width
#| echo: false
as.data.frame(t(summary(iris$Sepal.Width)))[,-1]
```
:::
:::

\vspace{4 mm}







